Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-08-26 tex/paper.tex
updating paper.tex to current text, adding Tikz drawing

		\plotone{figures/heating_functions.pdf}

@@

		\plotone{figures/em_grid_single_a25.pdf}

@@

		\plotone{figures/em_grid_electron_a25.pdf}

@@

		\plotone{figures/em_grid_ion_a25.pdf}

@@

		\plotone{figures/nT_sample_curves_tn2500_electron.pdf}

@@

		\plotone{figures/em_slope_varying_bounds.pdf}

@@

		\plottwo{figures/ratio_hist_alpha_single_T1.pdf}{figures/ratio_hist_twait_single_T1.pdf}

@@

		\plottwo{figures/ratio_hist_alpha_electron_T1.pdf}{figures/ratio_hist_twait_electron_T1.pdf}

@@

		\plottwo{figures/ratio_hist_alpha_ion_T1.pdf}{figures/ratio_hist_twait_ion_T1.pdf}

>>>>

		\plotone{../results/heating_functions.pdf}

@@

		\plotone{../results/em_grid_single_a25.pdf}

@@

		\plotone{../results/em_grid_electron_a25.pdf}

@@

		\plotone{../results/em_grid_ion_a25.pdf}

@@

		\plotone{../results/nT_sample_curves_tn2500_electron.pdf}

@@

		\plotone{../results/em_slope_varying_bounds.pdf}

@@

		\plottwo{../results/ratio_hist_alpha_single_T1.pdf}{../results/ratio_hist_twait_single_T1.pdf}

@@

		\plottwo{../results/ratio_hist_alpha_electron_T1.pdf}{../results/ratio_hist_twait_electron_T1.pdf}

@@

		\plottwo{../results/ratio_hist_alpha_ion_T1.pdf}{../results/ratio_hist_twait_ion_T1.pdf}
